### 2019-04-29 tii/tex/optimization.tex
Submit version 1.0

From the perspective of reduce task, SCache provides an API named $getBlock$ to replace the original implementation of shuffle read. 
With the precondition of shuffle data pre-fetching, 
the $getBlock$ leverages the memory copy to fetch the shuffle data from the local memory of SCache.
% Instead, the original implementation of shuffle read will trigger an all-to-all network transfer that keeps CPU idle.
%To this end, all I/O operations are managed outside of the DAG framework, and the slot is occupied only by the CPU intensive phases of task.
\subsection{Pre-schedule with Application Context}
The pre-scheduling and pre-fetching are the most critical aspects of the optimization. 
The task-node mapping is not determined until tasks are scheduled by the scheduler of DAG framework. 
Once the tasks are scheduled, the slots will be occupied to launch them. 
On the other hand, the shuffle data cannot be pre-fetched without the awareness of task-node mapping.
We propose a co-scheduling scheme with two heuristic algorithms (Algorithm \ref{hminheap}, \ref{mhminheap}). 
That is, the task-node mapping is established a priori, and then it is enforced by the co-scheduler when the DAG framework starts task scheduling. 
% We explore several pre-scheduling schemes in different scenarios, and evaluate the performance calculating the improvement of reduce tasks completion time with trace of OpenCloud \cite{opencloudtrace}. We first emulate the scheduling algorithm of Spark to schedule the reduce tasks of one job, and take the bottleneck of the task set as the completion time. Then we remove the shuffle read time as the assumption of shuffle data pre-fetch and emulate under different schemes. The result is shown in \ref{fig:sim}.
% \begin{figure*}
% 	\centering
% 	\begin{minipage}{0.34\linewidth}
% 		\begin{figure}[H]
% 			\includegraphics[width=\textwidth]{fig/shuffle_size}
% 			\caption{Shuffle Size Comparing with Input Size}
% 			\label{fig:shuffle_size}
% 		\end{figure}
% 	\end{minipage}
% 	\begin{minipage}{0.65\linewidth}
% 		\begin{figure}[H]
% 			\begin{subfigure}{0.5\textwidth}
% 				\includegraphics[width=\linewidth]{fig/reduce_cdf}
% 				\caption{Shuffle Time Fraction CDF}
% 				\label{fig:cdf}
% 			\end{subfigure}	
% 			\begin{subfigure}{0.5\textwidth}
% 				\includegraphics[width=\linewidth]{fig/sim}
% 				\caption{Stage Completion Time Improvement}
% 				\label{fig:sim}
% 			\end{subfigure}	
% 			\caption{Emulate Result of OpenCloud Trace}
% 		\end{figure}
% 	\end{minipage}
% \end{figure*}
% \begin{figure}
\subsubsection{Problem of Random Mapping}\label{randomassign}
The simplest way of pre-scheduling is mapping tasks to nodes randomly and evenly. 
In order to evaluate the effectiveness of random mapping, we use traces from OpenCloud\footnote{\label{fn:trace}http://ftp.pdl.cmu.edu/pub/datasets/hla/dataset.html} for the simulation.
% Note that most of the traces from OpenCloud are shuffle-light workload as shown in Figure \ref{fig:cdf}. 
The average shuffle read time is $3.2\%$ of total reduce completion time.

@@

To handle this corner case, we introduce another methodology, named \emph{weighted reservoir sampling}, as a substitution of linear regression. 
Note that linear regression will be replaced only when a RangePartitioner or a customized non-hash partitioner occurs. 
For each map task, we use classic reservoir sampling to randomly pick $s \times p$ of samples, where $p$ is the number of reduce tasks and $s$ is a tunable number. 
After that, the map function is called locally to process the sampled data (\textit{Sampling} in Figure \ref{fig:shuffle}). 
Finally, the partitioned outputs are collected with the $InputSize_j$ as the weight of the samples.
Note that sampling does not consume the input data of map tasks. 
The $BlockSize_{ji}$ can be calculated by:
\begin{equation}
\label{equationsample}
\begin{aligned}
	BlockSize_{ji} &= {{InputSize_j \times \frac{sample_i}{s \times p}}} \\
	sample_i &= \text{number of samples for $reduce_i$}
\end{aligned}
\end{equation}
% The classic reservoir sampling is designed for randomly choosing \textit{k} samples from \textit{n} items, where \textit{n} is either a very large or an unknown number \cite{reservoir}. 
In Figure \ref{fig:range_pre_sample}, when $s$ is set to $3$, the result of sampling prediction is much better than linear regression. 
The variance of the normalization between sampling prediction and reduce distribution is because the standard deviation of the prediction results is relatively small compared to the average prediction size, which is $0.0015$ in this example. 
Figure \ref{fig:prediction_relative_error} further proves that the sampling prediction can provide precise result even in the dimension of absolute input size of reduce task. 
On the other hand, the result of linear regression comes out with a large relative error. 
Though the weighted reservoir sampling is precise, it also introduced extra overhead. 
We will show the overhead evaluation of sampling in Section \ref{evaluation}.
% {\color{blue}
% Figure \ref{fig:prediction_relative_error} proves that the sampling prediction can provide much more accurate result than the linear regression. 
% We will show the overhead evaluation of sampling in Section \ref{evaluation}. 
% }

@@

% \ifrevision
% \marginpar{\tiny PC2,C1,D7/9,E4}
% \fi
As long as the input sizes of reduce tasks are available, the pre-scheduling is a classic scheduling problem without considering the data locality. 
But ignoring the data locality can introduce extra network transfer. 
In order to balance load while minimizing the network traffic, we present the Heuristic MinHeap scheduling algorithm (Algorithm \ref{hminheap}).

>>>>

From the perspective of reduce task, SCache provides an API named $getBlock$ to replace the original implementation of shuffle read. 
With the precondition of shuffle data pre-fetching, 
the $getBlock$ leverages the memory copy to fetch the shuffle data from the local memory of SCache.
% Instead, the original implementation of shuffle read will trigger an all-to-all network transfer that keeps CPU idle.
%To this end, all I/O operations are managed outside of the DAG framework, and the slot is occupied only by the CPU intensive phases of task.
\subsection{Pre-scheduling with Application Context}
The pre-scheduling and pre-fetching are the most critical aspects of the optimization. 
The task-node mapping is not determined until tasks are scheduled by the scheduler of DAG framework. 
Once the tasks are scheduled, the slots will be occupied to launch them. 
On the other hand, the shuffle data cannot be pre-fetched without the awareness of task-node mapping.
We propose a co-scheduling scheme with two heuristic algorithms (Algorithm \ref{hminheap}, \ref{mhminheap}). 
That is, the task-node mapping is established a priori, and then it is enforced by the co-scheduler when the DAG framework starts task scheduling. 
% We explore several pre-scheduling schemes in different scenarios, and evaluate the performance calculating the improvement of reduce tasks completion time with trace of OpenCloud \cite{opencloudtrace}. We first emulate the scheduling algorithm of Spark to schedule the reduce tasks of one job, and take the bottleneck of the task set as the completion time. Then we remove the shuffle read time as the assumption of shuffle data pre-fetch and emulate under different schemes. The result is shown in \ref{fig:sim}.
% \begin{figure*}
% 	\centering
% 	\begin{minipage}{0.34\linewidth}
% 		\begin{figure}[H]
% 			\includegraphics[width=\textwidth]{fig/shuffle_size}
% 			\caption{Shuffle Size Comparing with Input Size}
% 			\label{fig:shuffle_size}
% 		\end{figure}
% 	\end{minipage}
% 	\begin{minipage}{0.65\linewidth}
% 		\begin{figure}[H]
% 			\begin{subfigure}{0.5\textwidth}
% 				\includegraphics[width=\linewidth]{fig/reduce_cdf}
% 				\caption{Shuffle Time Fraction CDF}
% 				\label{fig:cdf}
% 			\end{subfigure}	
% 			\begin{subfigure}{0.5\textwidth}
% 				\includegraphics[width=\linewidth]{fig/sim}
% 				\caption{Stage Completion Time Improvement}
% 				\label{fig:sim}
% 			\end{subfigure}	
% 			\caption{Emulate Result of OpenCloud Trace}
% 		\end{figure}
% 	\end{minipage}
% \end{figure*}
% \begin{figure}
\subsubsection{Problem of Random Mapping}\label{randomassign}
The simplest way of pre-scheduling is mapping tasks to nodes randomly and evenly. 
In order to evaluate the effectiveness of random mapping, we use traces from OpenCloud\footnote{\label{fn:trace}http://ftp.pdl.cmu.edu/pub/datasets/hla/dataset.html} for the simulation.
% Note that most of the traces from OpenCloud are shuffle-light workload as shown in Figure \ref{fig:cdf}. 
The average shuffle read time is $3.2\%$ of total reduce completion time.

@@

To handle this corner case, we introduce another methodology, named \emph{weighted reservoir sampling}, as a substitution of linear regression. 
Note that linear regression will be replaced only when a RangePartitioner or a customized non-hash partitioner occurs. 
For each map task, we use classic reservoir sampling to randomly pick $s \times p$ of samples, where $p$ is the number of reduce tasks and $s$ is a tunable number. 
After that, the map function is called locally to process the sampled data (\textit{Sampling} in Figure \ref{fig:shuffle}). 
Finally, the partitioned outputs are collected with the $InputSize_j$ as the weight of the samples.
Note that sampling does not consume the input data of map tasks. 
The $BlockSize_{ji}$ can be calculated by:
\begin{equation}
\label{equationsample}
\begin{aligned}
	BlockSize_{ji} &= {{InputSize_j \times \frac{sample_i}{s \times p}}} \\
	sample_i &= \text{number of samples for $reduce_i$}
\end{aligned}
\end{equation}
% The classic reservoir sampling is designed for randomly choosing \textit{k} samples from \textit{n} items, where \textit{n} is either a very large or an unknown number \cite{reservoir}. 
In Figure \ref{fig:range_pre_sample}, when $s$ is set to $3$, the result of sampling prediction is much better than linear regression. 
The variance of the normalization between sampling prediction and reduce distribution is because the standard deviation of the prediction results is relatively small compared to the average prediction size, which is $0.0015$ in this example. 
Figure \ref{fig:prediction_relative_error} further proves that the sampling prediction can provide precise result even in the dimension of absolute input size of reduce task. 
On the other hand, the result of linear regression comes out with a large relative error. 
Though the weighted reservoir sampling is precise, it also introduces extra overhead. 
We will show the overhead evaluation of sampling in Section \ref{evaluation}.
% {\color{black}
% Figure \ref{fig:prediction_relative_error} proves that the sampling prediction can provide much more accurate result than the linear regression. 
% We will show the overhead evaluation of sampling in Section \ref{evaluation}. 
% }

@@

% \ifrevision
% \marginpar{\tiny PC2,C1,D7/9,E4}
% \fi
As long as the input sizes of reduce tasks are available, the pre-scheduling is a classic scheduling problem without considering the data locality. 
But ignoring the data locality can introduce extra network transfer. 
In order to balance load while minimizing the network traffic, we present the Heuristic MinHeap Scheduling algorithm (Algorithm \ref{hminheap}).
